Accelerated evolution of convective simulations

### 2018-05-30 referee_process/first_submission/referee_response.tex

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Editor,
$\,$\newline

\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}

\begin{singlespace}
Short cover letter blah blah.

$\,$\newline
\noindent
Sincerely,

Evan H. Anders, Benjamin P. Brown, \& Jeffrey S. Oishi

%\end{singlespace}

$\,$
\newline
$\,$
\newline
\noindent
\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent

\begin{myquotation}
This paper describes a technique for accelerating the convergence to
thermal equilibrium in convective DNS simulations where such
convergence from an initial conductive state would be long. The
technique is essentially to evolve a DNS for for a while, collect the
background state non-equilibrium fluxes, and then solve a mean field
boundary value problem with scaled version of these fluxes for a new
background state in thermal equilibrium, then use this to restart the
DNS. These, or very similar techniques, have been used by many in the
past, although to my knowledge, as the authors here also claim, they
have not been explicitly written down in a paper. The authors have
gone to the trouble of doing this, not only providing a fairly
detailed prescription of the technique, but also some evidence of its
usefulness, albeit in a very simple case where it will definitely work
which is perhaps not totally representative. I guess I think this
paper is overall worthwhile, since it provides a place for newcomers
to the business to find some potentially time-saving help, even though
the ideas are not original. I think the most important issue with this
paper is that its claims of more universal applicability are somewhat
naive. I would suggest they temper these assertions substantially.
\end{myquotation}
So this is the summary / takeaway paragraph. I think we need to
in some way \emph{prove} that such a prescription can be useful in
more complex situations. This is one of the biggest points we need to
address from this referee report: either temper our claims or prove them.

\begin{myquotation}
Basic questions:

How confident can one be that the BVP puts you closer to a nonlinear
saturated state that where you were? For example, in highly nonlinear
(turbulent) problems, there may be multiple states, maybe even
multiple stable states, with different background properties. Is it
possible to guarantee that you are not putting the system into an
equilibrium but unstable state, from which an equally long evolution
to a stable state is required? For the simple problems shown here,
this is perhaps not likely, but for very high degrees of turbulence,
or situations where unknown instabilities may exist, this process may
not be so successful perhaps? This is again a factor in my hesitation
about the total applicability of this technique across many problems
beyond the one the authors present.
\end{myquotation}
Yeah, this is a good question. I don't know the answer to this immediately.
I think we need to make some sort of clear distinction between ``AE works
perfectly always'' and ``AE is better than running from initial conditions.''

\begin{myquotation}
Here are some more comments in chronological order, not order of
importance.

Abstract and Intro:

The authors come from an astrophysical convection background where the
Peclet number is generally high and where these techniques are useful.
They need to be careful to be clear that the convection they are
talking about is high Pe, the parameter that describes the separation
of overturning and thermal diffusion timescales. These techniques will
not be useful (or required) for low Pe number situations.
\end{myquotation}

Yeah, that's fair. Peclet number is actually what matters, not Re, for
this problem. We should say that, and perhaps we should report Pe if we
ever report one or the other.

\begin{myquotation}
Section II.

After (4): The expression for delta T\_0 assumes that the background
temperature gradient is constant, which has not been introduced yet.

The sentence “ Our choice of the thermal boundary conditions in Eqn.
(9 ) was motivated by the fact that accelerated evolution is simpler
when both the thermal profile and the flux through the domain are
fixed at a boundary” is never revisited or explained, unless I missed
it?
\end{myquotation}
Two small fixes.

\begin{myquotation}
Section III.

The assumption after equation (10) that the convective region will NOT
change substantially is a BIG assumption that allows this technique to
work. In a situation where nonlinearities affect the extent of the
convective region (e.g. penetrative convection), our anywhere else
where the active region varies (e.g. an instability), this technique
will have problems. More on this later.

Equations (12-13): These are essentially steady state, mean field
equations, with approximated fluxes for the later (solved) state. Is
the prescription for the approximated fluxes in (11) going to work for
all problems? It does so for the case examined, but this case has a
simple background temperature gradient. Would this work for more
complicated problems, for example, with a non-constant DT\_0/dz? What
about the cases that are NOT symmetric (i.e. periodic in the
horizontal where the mean field equations contain some other terms?
\end{myquotation}
Yeah, this should work for non-constant DT/Dz. I designed the layout of the
paper with internally heated systems in mind, where the background temperature
gradient is linear. This is the reason for the generality of the $\xi$
and $F_{tot}$ construction. Should say so explicitly, maybe?

\begin{myquotation}
Last para: the authors say “proper” profile, but this is an
approximate thermodynamic background profile, essentially the first
iterate in an iteration scheme. Perhaps proper is not the right word?
\end{myquotation}
Proper probably isn't the right word.

\begin{myquotation}
IV:

I don’t understand ``$10^{3+2/3}$''? Why is written like this?
\end{myquotation}
I think that's a typo from a previous draft.

\begin{myquotation}
I am not convinced that the whole ``2D and 3D scaling laws'' section
adds anything at all to this paper. It shows that this technique can
be used but so does the single example that is interrupted by this
piece. It is somewhat interesting for the scaling laws found
themselves, but it sounds like this should be in a different paper
because there is not enough explanation to understand things totally
here. I feel like the examples before and after this section are
sufficient to make the point about the AE scheme.
\end{myquotation}
Fair. It's sort of off-topic. The purpose of that figure is to show that
AE works across Ra, not to show that we get correct scaling laws. We
should address this.

\begin{myquotation}
When discussing the PDFs, the author refer to the “modes” of the PDF?
This sounds a bit odd to me. Do they mean the peaks? The phrase
“temperature fluctuations off of the modes” is particularly baffling!
\end{myquotation}
Yeah, I mean mode as in ``the mode of the PDF'', so the max. I can say max
or peak.

\begin{myquotation}
The fact that the mean temperature profile is off by a constant factor
almost everywhere is a bit disturbing, even if the factor is small.
Does continued iteration of AE not get rid of this? If not, then this
is significant, because it would take a thermal relaxation time again
to correct this issue.
\end{myquotation}
This is the second biggest point in this referee report. We need to talk about this
and figure out how to address it.

\begin{myquotation}
I felt like I wanted a section at the end of this section that
described how much the AE saved in computational time and wall time
over SE. There is a bit of it here, and some of it in the discussion,
and some more details in the appendix, which seems a bit scattered. I
would be tempted to agglomerate it all here in a separate section.
\end{myquotation}
Fair, let's figure out how to consolidate this and present it in a meaningful way.

\begin{myquotation}
V.

This is the section I have most issues with.

The example performed was the most likely to succeed. The 2D cases
were essentially rolls. Were the 3D cases still essentially 2D rolls
too (since the scalings came out the same)? What about larger aspect
ratio and more turbulence cases where the dynamics would be more
complex? Keeping things smooth certainly enhances the likelihood of a
simple scaling of the nonlinear fluxes working.

I think the projections for more complicated problems mentioned are
naive. If there is any nonlinear adjustment to the convective region,
e.g. penetrative convection, then the technique is far less likely to
be simply successful in the current form. The assumption of fully
convective and thermal boundary layers remaining in place is a big
one, and this is not really acknowledged. The authors do mention
penetrative convection and do indeed say that only a stiff case would
work under these premises, but this is a bit hidden, I think, and
needs to be emphasized more. For example, the penetrative ice-water
problem even in Boussinesq would not work well with this technique I
think, since the penetrative region can deepen dramatically, and
adjust the radiative flux to match the substantially changed
convective flux.

Furthermore, the compressible case is much more danger prone than
envisioned here. I suspect that in the iteration to accelerate, any
mismatch in the fluctuations and the estimated means in the DNS will
lead to major transients in the form of sound waves, which can totally
destroy a compressible evolution by reducing the tilmestep
substantially, so this technique may have drawbacks if there is not
filtering of sound waves somehow. The authors have glossed over these
problems in their eagerness to extol the virtues of their scheme.

I think the claims of this method working in many more situations need
to be examined more thoroughly before being made so boldly here.
\end{myquotation}
We either need to back off on some of these claims, show that AE works
in a more complex situation, or temper these claims with warnings of
possible complications.

\noindent
\Large{\textbf{Response to second referee:}}\newline$\,$\newline\indent
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\item The authors should provide clarification on what the following terms mean: ``thermal equilibration'', ``thermally relaxed'', and ``thermal convergence''. Also, are these terms related to statistically steady state?
\item What is the ``Kelvin-Helmholtz timescale''?
\end{enumerate}
\end{myquotation}
We need to define these
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{2}
\item The authors note that the bootstrapping method is susceptible to hysteresis effects. They should provide examples of where such effects have been observed.
\end{enumerate}
\end{myquotation}
I know this from my own work. Shearing states are heavily susceptible to hysteresis, especially in stratified domains. I don't know of anywhere this is explicitly said in the literature.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{3}
\item It is true that direct numerical simulation of turbulent thermal convection is expensive. However, the highest Ra simulation run by Stevens et al. reaches a stationary state in a few hundreds of free-fall times. Hence, what is the necessity of running simulations for ``thousands or millions of free-fall times''?
\end{enumerate}
\end{myquotation}
Yeah, this is mostly only a problem in stratified cases. Actually, in general, I think this isn't a huge problem for constant temperature BCs, but it is for other types of BCs in RBC.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{4}
\item Presumably, the most important step in the “Accelerated convergence method” involves decreasing the heat flux through the top boundary so as to match it with the heat flux at the bottom boundary. This is achieved by introducing a function $\xi(z) \equiv  F_B/F_{tot}$. The following questions arise:
\begin{enumerate}
\item What is the functional form of $\xi(z)$? And where does the z-dependence come from?
\item Here, $F_{tot}$ is not really a constant, but depends on time. Hence, $\xi(z)$ should also be a function of time.
\item The “evolved” quantities are obtained by multiplying $\langle \bm{u} \times \bm{\omega} \rangle$ and $F_E$ by $\xi(z)$. Can this construction be rigorously justified? I would like the authors to provide more details on how they arrived at this step.
\end{enumerate}
\end{enumerate}
\end{myquotation}
We need to make all of this clearer, apparently. The fact that it's a function of $t$ is an important change.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{5}
\item The assumption that convection at early times occupies roughly the same volume as convection in the stationary state is acceptable. However, there is also the possibility that instead of decreasing the heat flux at the top one could increase it at the bottom? The boundary condition for T1 at the bottom surface is
$$
\frac{\partial T_1}{\partial z} = 0
$$
So, the imposed heat flux at the bottom is 0.
\end{enumerate}
\end{myquotation}
I think there's a fundamental misunderstanding of what's happening with the boundary conditions here. I need to type up a clear response to the referee, and also make sure that I make this clear in the paper.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{6}
\item Could the authors construct plots of Nu vs. t (like in figure 2) for both AE and SE starting from t = 0? I would like to understand how Nu(t) evolves with time in the AE cases.
\end{enumerate}
\end{myquotation}
Sure, we can do send the referee that plot. I don't think we should change the 
figure as is, though.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{7}
\item I diasgree with the authors’ statement that “Previous studies in 2D convection may have avoided these time-varying Nu states by using bootstrapping techniques...” If one were to measure Nu(t) in the interior, then the sign of Nu would fluctuate between positive and negative. However, the time average would be always be positive. (This I know from my own work.)
\end{enumerate}
\end{myquotation}
Hmm. Interesting point. Need to think about how to respond to this carefully.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{8}
\item Have the authors studied convection with fixed temperature and no-slip conditions at the top and bottom surfaces? Have they compared the AE and SE results for that case?
\end{enumerate}
\end{myquotation}
We have not. We've used no-slip at both surfaces, but only mixed thermal boundary conditions. We can do fixed T boundary conditions, but that would require a different treatment of the total flux.

\end{singlespace}

\bibliography{../../biblio.bib}
\end{document}

### 2018-06-07 tex/bvp_paper.tex
big commit of referee work

Unfortunately, convective systems are stiff in more than one timescale and
generally evolve over the course of thermal
timescales, which are often much larger than all relevant
dynamical timescales. Transport by convection is a highly nonlinear process,
and this makes addressing the stiffness much more challenging; even fully
implicit  methods remain bound by the nonlinear flow timescales
\cite{viallet&all2011, viallet&all2013, viallet&all2016}. 
Resolving dynamics in atmospheres which are sufficiently
thermally relaxed remains a challenging problem.
Solar convection is a prime example of this phenomenon, as
dynamical timescales in the solar convective zone are relatively short 
(convection overturns every $\sim 5$ minutes at the solar surface)
compared to the Sun's Kelvin-Helmholtz timescale of
$3 \cdot 10^7$ years \cite{stix2003}.  
In such a system, it is impossible to resolve the convective dynamics while also
meaningfully evolving the thermal structure of the system using
traditional timestepping techniques alone.
As modern simulations aim to model natural convection
in the high-Rayleigh-number (Ra) regime,
the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
becomes intractably large compared to dynamical timescales 
such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
\cite{anders&brown2017}, 
\begin{equation}
\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
\end{equation}
Furthermore, as dynamical and thermal timescales separate, 
simulations become more turbulent. Capturing appropriately resolved
turbulent motions requires finer grid meshes and smaller timesteps.
Thus, the progression of simulations into the high-Ra
regime of natural convection is slowed by two simultaneous effects: timestepping
through a single convective overturn time becomes more computationally expensive
and the number of overturn times required for systems to reach thermal equilibration
grows.

The vast difference between convective and thermal timescales has long plagued
numericists studying convection, and an abundance of approaches has been employed to
study thermally converged solutions. One popular method for accelerating the convergence
of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
fields in a converged solution at low Ra as initial conditions for a simulation at high
Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
but it is not without its faults.  Bootstrapped solutions are susceptible to hysteresis
effects, in which large-scale convective structures present in the
low Ra solution imprint onto the dynamics of the new, high Ra solution. 
Another commonly-used tactic in
moderate-Ra simulations is to first solve a simple model of the system in question,
and then use the solution of that model as initial conditions for full nonlinear
direct numerical simulations. For example, past studies have used initial conditions from
a linear eigenvalue solve \cite{hurlburt&all1984} in plane-parallel studies, or
axisymmetric solutions in studies of convection in 3D cylinders \cite{verzicco&camussi1997}. 
In other systems, particularly when convective zones are adjacent to stable regions,
authors often choose initial conditions which are not in a classic, hydrostatic,
conductive state. Rather, either through knowledge of low-Ra solutions \cite{couston&all2017}
or broader convective theories such as Mixing Length Theory
\cite{brandenburg&all2005}, initial conditions can be adjusted such that the stratification
within the convective domain is closer to an equilibrium state than the largely
unstable hydrostatic state.

Despite the numerous methods that have been used,
the most straightforward way to achieve a thermally converged solution
is to evolve a convective simulation through a thermal timescale. Some modern
studies do just that \cite{featherstone&hindman2016}.
Such evolution is computationally 
\emph{expensive}, and state-of-the-art simulations at the highest values of Ra
can only reasonably be run
for hundreds of freefall timescales \cite{stevens&all2011}, much less the
thousands or millions of freefall times required for thermal convergence.

@@

\section{Experiment}
\label{sec:experiment}
In this work we study a simple form of thermal convection:
incompressible \RB convection under the Oberbeck-Boussinesq approximation,
such that the fluid
has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$,
except in the buoyancy term, where it is $\rho = \rho_0(1  - \alpha T_1)$.
The gravitational acceleration, $\bm{g} = - g\bm{\hat{z}}$, is constant.
The equations of motion are \cite{spiegel&veronis1960}:
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
where $\bm{u} = u\bm{\hat{x}} + v\bm{\hat{y}} + w\bm{\hat{z}}$ is the velocity, 
$T = T_0(z) + T_1(x, y, z, t)$ are the initial and fluctuating components of temperature, 
and $P$ is the kinematic pressure.
We non-dimensionalize these equations such that
length is in units of the layer height ($L_z$),
temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \partial_z T_0$), 
and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \partial_z T_0}$).
By these choices, one time unit is a freefall time ($t_{\text{ff}} = L_z/v_{\text{ff}}$).
We introduce a reduced kinematic pressure,
$\varpi \equiv (P / \rho_0 + \phi + |\bm{u}|^2 / 2) / v_{\text{ff}}^2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. 
In non-dimensional form, and substituting 
$\bm{u}\cdot\grad\bm{u} = \grad(|\bm{u}|^2/2) - \bm{u}\times(\grad\times\bm{u})$
and $\grad^2\bm{u} = -\grad\times(\grad\times\bm{u})$, Eqns.~\ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
become
\begin{align}
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} &= \bm{u}\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} &= - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters $\mathcal{R}$ and $\mathcal{P}$ 
are set by the Rayleigh (Ra) and Prandtl (Pr) numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
\end{equation}
We hold Pr $= 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.
$\mathcal{P}$ and $\mathcal{R}$ are related to the inverse Reynolds and Peclet numbers of the
evolved flows.

@@

Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  
We study 2D and 3D convection in which the domain is a cartesian box, 
whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
where $\Gamma = 2$ is the aspect ratio, as has been previously studied
\cite{goluskin&all2014, johnston&doering2009}. 
In 2D simulations, we set $v = \partial_y = 0$.
We specify no-slip, impenetrable boundary conditions at both the top and
bottom boundary,
\begin{equation}
u = v = w = 0 \, \, \text{at}\,\,z = \pm 1/2,
\label{eqn:vel_bcs}
\end{equation}
and we use mixed thermal boundary conditions, such that
\begin{equation}
T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
\label{eqn:temp_bcs}
\end{equation}
For this choice of boundary conditions, the critical value of Ra at which
the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$ \cite{goluskin2016}, and the
supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
Studies of convection which aim to model
astrophysical systems such as stars often employ mixed thermal
boundary conditions, as we do here \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
Our choice of the thermal boundary conditions in Eqn.~(\ref{eqn:temp_bcs}) 
was motivated by the fact that accelerated evolution is simpler when both the
thermal profile and the flux through the domain are fixed at a boundary.

@@

In a time-stationary state, the horizontal- and time-average of
Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
vanish due to symmetry, are
\begin{gather}
\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y, \text{ ev}},
	\label{eqn:bouss_BVP_momentum}
\\
\frac{\partial}{\partial z}\text{F}_{\text{E, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
	\label{eqn:bouss_BVP_energy}
\end{gather}
Here, we construct $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
\xi(z) \angles{\bm{u}\times\bm{\omega}}_{x, y}$ and $\text{F}_{\text{E, ev}} = \xi(z) \text{F}_{\text{E}}$
from our unevolved state, and solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
Convective flows
are perturbations around a thermal profile defined by these equations in the proper evolved, 
statistically stationary state. Furthermore, under the proper specification of
F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
\emph{the mean thermodynamic structure of the system is fully specified}.

>>>>

Unfortunately, astrophysical convective systems are stiff in more than one 
timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
diffusion timescale to the advective velocity timescale, is large.
This further stiffness arises as a result of the thermodynamic structure 
evolving over the course of thermal timescales, not the short dynamical advective
timescales. In order to reach thermal equilibration, a steady state in which
the thermal structure of the atmosphere is no longer evolving over time,
many dynamical timescales must be simulated.
Transport by convection is a highly nonlinear process,
and this makes addressing the stiffness much more challenging; even fully
implicit  methods remain bound by the nonlinear flow timescales
\cite{viallet&all2011, viallet&all2013, viallet&all2016}. 
Resolving dynamics in atmospheres which are sufficiently
thermally equilibrated remains a challenging problem.
Solar convection is a prime example of this phenomenon, as
dynamical timescales in the solar convective zone are relatively short 
(convection overturns every $\sim 5$ minutes at the solar surface)
compared to the Sun's thermal evolution timescale, which is O($10^7$) years
\cite{stix2003}.  
In such a system, it is impossible to resolve the convective dynamics while also
meaningfully evolving the thermal structure of the system using
traditional timestepping techniques alone.
As modern simulations aim to model natural, high-Pe convection
in the high-Rayleigh-number (Ra) regime,
the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
becomes intractably large compared to dynamical timescales 
such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
\cite{anders&brown2017}, 
\begin{equation}
\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
\end{equation}
Furthermore, as dynamical and thermal timescales separate, 
simulations become more turbulent. Capturing appropriately resolved
turbulent motions requires finer grid meshes and smaller timesteps.
Thus, the progression of simulations into the high-Ra
regime of natural convection is slowed by two simultaneous effects: timestepping
through a single convective overturn time becomes more computationally expensive
and the number of overturn times required for systems to reach thermal equilibration
grows.

The vast difference between convective and thermal timescales has long plagued
numericists studying convection, and an abundance of approaches has been employed to
study thermally equilibrated solutions. One popular method for accelerating the convergence
of high-Ra solutions is by ``bootstrapping'' -- the process of using the flow
fields in a converged solution at low Ra as initial conditions for a simulation at high
Ra.  This method has been used with great success \cite{johnston&doering2009, verzicco&camussi1997},
but it is not without its faults.  In systems in which there are multiple
stable solutions, such as a roll state and a shearing state of convection,
the large-scale convective structures present in the
low Ra solution imprint onto the dynamics of the new, high Ra solution. 
It is possible that this puts the high Ra solution into a different stable state
than it would naturally reach from an initial, hydrostatically stable configuration.
Another commonly-used tactic in
moderate-Ra simulations is to first solve a simple model of the system in question,
and then use the solution of that model as initial conditions for full nonlinear
direct numerical simulations. For example, past studies have used initial conditions from
a linear eigenvalue solve \cite{hurlburt&all1984} in plane-parallel studies, or
axisymmetric solutions in studies of convection in 3D cylinders \cite{verzicco&camussi1997}. 
In other systems, particularly when convective zones are adjacent to stable regions,
authors often choose initial conditions which are not in a classic, hydrostatic,
conductive state. Rather, either through knowledge of low-Ra solutions \cite{couston&all2017}
or broader convective theories such as Mixing Length Theory
\cite{brandenburg&all2005}, initial conditions can be adjusted such that the stratification
within the convective domain is closer to an equilibrium state than the largely
unstable hydrostatic state.

Despite the numerous methods that have been used,
the most straightforward way to achieve a thermally equilibrated solution
is to evolve a convective simulation through a thermal timescale. Some modern
studies do just that \cite{featherstone&hindman2016}.
Such evolution is computationally 
\emph{expensive}, and state-of-the-art simulations at the highest values of Ra
can only reasonably be run
for hundreds of freefall timescales \cite{stevens&all2011}, much less the
thousands or millions of freefall times required for thermal equilibration.

@@

\section{Experiment}
\label{sec:experiment}
In this work we study a simple form of thermal convection:
incompressible \RB convection under the Oberbeck-Boussinesq approximation,
such that the fluid
has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$,
except in the buoyancy term, where it is $\rho = \rho_0(1  - \alpha T_1)$.
The gravitational acceleration, $\bm{g} = - g\bm{\hat{z}}$, is constant.
The equations of motion are \cite{spiegel&veronis1960}:
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
where $\bm{u} = u\bm{\hat{x}} + v\bm{\hat{y}} + w\bm{\hat{z}}$ is the velocity, 
$T = T_0(z) + T_1(x, y, z, t)$ are the initial and fluctuating components of temperature, 
and $P$ is the kinematic pressure. The initial temperature profile decreases
linearly with height.
We non-dimensionalize these equations such that
length is in units of the layer height ($L_z$),
temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \partial_z T_0$), 
and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \partial_z T_0}$).
By these choices, one time unit is a freefall time ($t_{\text{ff}} = L_z/v_{\text{ff}}$).
We introduce a reduced kinematic pressure,
$\varpi \equiv (P / \rho_0 + \phi + |\bm{u}|^2 / 2) / v_{\text{ff}}^2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. 
In non-dimensional form, and substituting 
$\bm{u}\cdot\grad\bm{u} = \grad(|\bm{u}|^2/2) - \bm{u}\times(\grad\times\bm{u})$
and $\grad^2\bm{u} = -\grad\times(\grad\times\bm{u})$, Eqns.~\ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
become
\begin{align}
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} &= \bm{u}\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} &= - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters $\mathcal{R}$ and $\mathcal{P}$ 
are set by the Rayleigh (Ra) and Prandtl (Pr) numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
\end{equation}
We hold Pr $= 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.
$\mathcal{P}$ and $\mathcal{R}$ are related to the inverse Reynolds and Peclet numbers of the
evolved flows.

@@

Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  
We study 2D and 3D convection in which the domain is a cartesian box, 
whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
where $\Gamma = 2$ is the aspect ratio, as has been previously studied
\cite{goluskin&all2014, johnston&doering2009}. 
In 2D simulations, we set $v = \partial_y = 0$.
We specify no-slip, impenetrable boundary conditions at both the top and
bottom boundary,
\begin{equation}
u = v = w = 0 \, \, \text{at}\,\,z = \pm 1/2,
\label{eqn:vel_bcs}
\end{equation}
and we use mixed thermal boundary conditions, such that
\begin{equation}
T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
\label{eqn:temp_bcs}
\end{equation}
For this choice of boundary conditions, the critical value of Ra at which
the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$ \cite{goluskin2016}, and the
supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
Studies of convection which aim to model
astrophysical systems such as stars often employ mixed thermal
boundary conditions, as we do here \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
Our choice of the thermal boundary conditions in Eqn.~(\ref{eqn:temp_bcs}) 
was motivated by the fact that accelerated evolution is simpler when both the
thermal profile and the flux through the domain are fixed at a boundary 
(see section \ref{sec:ae}).

@@

In a time-stationary state, the horizontal- and time-average of
Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
vanish due to symmetry, are
\begin{gather}
\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y, \text{ ev}},
	\label{eqn:bouss_BVP_momentum}
\\
\frac{\partial}{\partial z}\text{F}_{\text{E, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
	\label{eqn:bouss_BVP_energy}
\end{gather}
Here, we construct $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
\xi(z) \angles{\bm{u}\times\bm{\omega}}_{x, y}$ and $\text{F}_{\text{E, ev}} = \xi(z) \text{F}_{\text{E}}$
from our unevolved state, and solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
Convective flows
are perturbations around a thermal profile defined by these equations in the proper evolved, 
statistically stationary state. Furthermore, under the proper specification of
F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
\emph{the mean thermodynamic structure of the system is fully specified}. 
Our choice of fixing the temperature at the top boundary and the flux at the bottom
boundary ensures that there is a unique solution for $T_1$ given the evolved
fluxes. If flux were fixed at both boundaries, there would be infinitely many
temperature solutions. If temperature were fixed at both boundaries, 
$\text{F}_{\text{B}}$ would not be precisely known \emph{a priori}.
